A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator

### 2016-11-13 paper3_manuscript.tex
20161113

\begin{document}
\begin{frontmatter}
\title{A New Dual Terminal SMC Design For Rigid Robotic Manipulator}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

\begin{abstract}
This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator. \textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual sliding mode surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme. We combine the adaptive technique with the proposed method to eliminate the bad effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.
\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; TSM; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}

\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}. Among these methods, the high-order SMC and super-twisting SMC work in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}. Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently. The normal linear SMC scheme completes the stabilization of the system dynamics. In the first step, the control inputs drive the system states onto the prescript sliding surfaces, and this stage is also called the reaching phase. Then the sliding mode dynamics work to drive the system states to the origins along the ideal surfaces in the second step, and this stage is usually called the sliding phase. The reaching phase  usually requires the states converge to the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability. To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the SMC design mentioned above, the most significant contributions of the TSM are introducing the finite time convergence to the sliding phase to complete the global finite time convergence. Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signals. Feng et al. presented a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}

\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time control theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}. This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent. In this paper, an integral sliding mode surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence. Moreover, nonsingularities of the TSM scheme, chattering suppressions, underactuated applications and input limitations are also considered in the scheme.}

\textcolor{red}{In this paper, the dual TSM (DTSM) control scheme is proposed for a class of second-order nonlinear systems with disturbances and uncertainties. The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly. For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we combine the hierarchical SMC scheme with the DTSM scheme to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses. A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration. The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM scheme, and the finite time convergences of the reaching and sliding phase are discussed. Furthermore, we provide the DTSM scheme with extra design parameters to obtain the MDTSM scheme, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section. In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out. Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.}
\section{Dual terminal SMC}\label{sec:2}
Consider a second-order nominal nonlinear system:
\begin{align}
\begin{split}
\dot x_1 &= x_2\\
\dot x_2 &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)u_1\\
\dot x_3 &= x_4\\
\dot x_4 &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2,\label{eq:second-order system}
\end{split}
\end{align}
where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i(t)$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances. For the system mentioned above, we can design the desired DTSM surface as:
\begin{align}
\bm s = [s_1,s_2]^T,
\end{align}
where
\begin{align}
\begin{split}
s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t)-x_3\\
s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t)+x_1.\label{eq:dual sliding surface}
\end{split}
\end{align}
\textcolor{red}{}$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar. For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s(t)$ is often abbreviated as $\bm s$.}

There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM scheme.
\begin{mylem}
As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive definite, satisfying following conditions:
\begin{align}
\dot V(t)\le -dV^\beta(t)\quad\forall t\ge t_0, V(t_0)\ge 0,
\end{align}
where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
\begin{align}
t_r \le t_0+\frac{V^{1-\beta}(t_0)}{d(1-\beta)}.
\end{align}\label{lemma:1}
\end{mylem}
\begin{mylem}
Consider a second-order system:
\begin{align}
\begin{split}
\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding surface}
\end{split}
\end{align}
and oen can select the Lyapunov function $V(t) = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
%since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
\begin{align}
%t_s\le t_0+\frac{2(x_1^2+x_2^2)^{1-\alpha}}{1-\alpha}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{1-\alpha},
\end{align}
where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding surface}) obtains:
\begin{align}
\dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding surface}
\end{align}
the convergence time of which is
\begin{align}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{d(1-\alpha)}.
\end{align}\label{lemma:2}
\end{mylem}
\textcolor{red}{For stabilization of the second-order system shown as~Eq. (\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
\begin{mythm}\label{theorem:1}DTSM Controller Design. The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
\begin{align}
\begin{split}
u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),\label{eq:DSM input}
\end{split}
\end{align}
where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value.
\end{mythm}
\begin{proof}
\textcolor{red}{According to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be design as
\begin{align}\begin{split}
u_1 &= u_{eq1}+u_{sw1}\\
u_2 &= u_{eq2}+u_{sw2}\notag
\end{split}\end{align}
where
\begin{align}\begin{split}
u_{eq1} &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
u_{eq2} &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2)\notag
\end{split}\end{align}
are the eauivalent control inputs to ensure $\dot s_1 = 0$ and $\dot s_2=0$, respectively, with $u_i = u_{eqi}$, $i=1,2$. The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the ideal sliding surface.}

Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative $\dot V$ can be written as

@@

Substituting inputs (\ref{eq:DSM input}) in~Eq. (\ref{eq:V_1}) yields

@@

Hence, the system (\ref{eq:second-order system}) converges to the desired surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory.\par
Once the system (\ref{eq:second-order system}) reaches the desired surface~(\ref{eq:dual sliding surface}), the entire system states are handled by the reduced system:

@@

where $\hat V(t) = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system. $t_r$ and $t_s$ stand for the reaching time and the sliding time, respectively. This completes the proof.}

@@

On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the surface design to improve the performance, and furthermore this modified method makes the design process more flexible. Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:

@@

s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3(t))-\lambda x_3\\
s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3(t))+\lambda x_1,\label{eq:modified dual sliding surface}

@@

where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal SMC inputs are formed in the following theorem.
\begin{mythm}\label{theorem:2}Modified Dual Terminal SMC Design.
The second-order system (\ref{eq:second-order system}) will reach the desired surface $\bm s = 0$ shown in~Eq. (\ref{eq:modified dual sliding surface}) in finite time. The states of the system will converge to zero along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:

@@

After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the reaching and sliding phases become regulatable, meaning that these parameters can adjust the convergence time analytically. Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergence time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed. Strictly speaking, it affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s = 0,\forall t\ge t_r$. Admittedly, the variety of $\lambda$ is only modestly helpful in this reaching time regulation due to its limited effect on $V(t_0)$. $\eta$ is said to be an ''reaching speed'' according to its function, a suitable selection of which will adjust the reaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the reaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.

@@

For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergence time as:

@@

The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs. Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition). For coping with the singularity, a nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.

@@

Considering the second-order system (\ref{eq:second-order system}), the TSM surface is designed as:

@@

and nonsingular inputs are given out directly as follows:

@@

where $sat(u_f,u_s)$ is a saturation function:

@@

-u_s\quad &u_f\le -u_s

@@

and $u_s>0$ is determined according to the requirements of the performance.\par
Adopting the control scheme mentioned above, the system~(\ref{eq:second-order system}) will converge to zero in finite time without any singularity occurring during the regulation process.

@@

Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select new inputs to complete the nonsingular MDTSM scheme. Introducing the saturation terms into the original inputs yields:

@@

one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using sliding mode technique.

@@

@@

In practice, the control input can not be very large due to the input limitation, such as the tension limitation in the deployment of the tethered satellite system~\cite{Ma201667}, and hence it is meaningful to adapt the proposed controllers for the system subjected to the input limitation. Consider a nominal second-order system subjected to the input limitation:

@@

Thanks to the above assumption, we give out the adaptive dual terminal SMC scheme.

@@

Consider a nonlinear system described as:

@@

where the condition of variables is same to the system~(\ref{eq:second-order system}). Construct the surface as:

@@

where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in the MDSM design. Adopting the equivalent control design method deduces the individual equivalent inputs:

>>>>

\begin{document}
\begin{frontmatter}
\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

\begin{abstract}
This paper proposes a dual terminal SMC scheme for the rigid robotic manipulator. \textcolor{red}{As a signiﬁcant novelty, the presented design technique integates the individual SM surfaces to achieve the finite time convergence of overall system states by utilizing specially designed construct, and accordingly the convergence time for the entire system is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue are solved by introducing the hierarchical methodology into the basic dual SMC scheme. Combining the adaptive technique with the proposed method eliminates the adverse effect caused by the input limitation in the rigious stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.
\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; TSM; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the bad effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the application of a SMC in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parameteric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and convergence speed design schemes~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering applications~\cite{fridman2011sliding}.}

\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}. Among these methods, the high-order SMC and super-twisting SMC work in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}. Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently. The normal linear SMC scheme completes the stabilization of the system dynamics. In the first step, the control inputs drive the system states onto the prescript sliding surfaces, and this stage is also called the reaching phase. Then the sliding mode dynamics work to drive the system states to the origins along the ideal surfaces in the second step, and this stage is usually called the sliding phase. The reaching phase  usually requires the states converge to the ideal sliding mode (SM) surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phaseis related to the designed ideal sliding surfaces closely, and trivial design techniques are can guarantee the asymptotically stability. To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the SMC design mentioned above, the most significant contributions of the TSM are introducing the finite time convergence to the sliding phase to complete the global finite time convergence. Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signals. Feng et al. presented a novel Lagrangian dynamic expression for the the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}

\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time control theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}. This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergence time in some extent. In this paper, an integral SM surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence. Moreover, nonsingularities of the TSM scheme, chattering suppressions, underactuated applications and input limitations are also considered in the scheme.}

\textcolor{red}{In this paper, the dual TSM (DTSM) control scheme is proposed for a class of second-order nonlinear systems with disturbances and uncertainties. The novel DTSM surface is exploited to achieve the finite time convergence, and the reaching and sliding times can both be calculated directly. For coping with the underacutated issue, cooperating with the hierarchical sliding surface design methodology, we combine the hierarchical SMC scheme with the DTSM scheme to develop a hierarchical dual TSM (HDTSM) control law to ensure the rigorous stability analyses. A modified DTSM (MDTSM) control scheme is presented to regulate the motion of the $n$-link robotic manipulators, and the case subjected to input limitations is also taken into consideration. The remained paper is organized as follows: Section~\ref{sec:2} introduces the DTSM scheme, and the finite time convergences of the reaching and sliding phase are discussed. Furthermore, we provide the DTSM scheme with extra design parameters to obtain the MDTSM scheme, which performs better in theoretical analyses; for stabilizing underactuated systems, the HDTSM design is also developed in this section. In Section~\ref{sec:3}, the MDTSM is applied to the motion control system of the $n$-link robotic  manipulator, and the stability analyses are also carried out. Section~\ref{sec:4} exhibits the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.}
\section{Dual terminal SMC}\label{sec:2}
Consider a nominal second-order nonlinear system:
\begin{align}
\begin{split}
\dot x_1 &= x_2\\
\dot x_2 &= f_1(\bm x,t)+g_1(\bm x,t)+b_1(\bm x,t)u_1\\
\dot x_3 &= x_4\\
\dot x_4 &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2,\label{eq:second-order system}
\end{split}
\end{align}
where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system state vector ; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$ and $t$; $u_i$, $i=1,2$ stands for the system input; $g_i(\bm x,t)$, $i=1,2$  is defined as the bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0, i=1,2$, meaning uncertainties and disturbances. For the system mentioned above, we can design the desired DTSM surface as:
\begin{align}
\bm s = [s_1,s_2]^T,
\end{align}
where
\begin{align}
\begin{split}
s_1 &= x_2+\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3-x_3\\
s_2 &= x_4+\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3+x_1.\label{eq:dual sliding surface}
\end{split}
\end{align}
\textcolor{red}{$sgn(x)$ is the sign function, and $0<\alpha<1$ is a positive scalar. For the sake of simplicity, the symbol $t$ is usually omitted in this paper, and it will appear once the derivation concerns for the factor of the time strictly, i.e., the desired sliding surface $\bm s(t)$ is often abbreviated as $\bm s$.}

There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM scheme.
\begin{mylem}
As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V$ is positive definite, satisfying following conditions:
\begin{align}
\dot V\le -dV^\beta\quad\forall t\ge t_0, V(t_0)\ge 0,
\end{align}
where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
\begin{align}
t_r \le t_0+\frac{V^{1-\beta}(t_0)}{d(1-\beta)}.
\end{align}\label{lemma:1}
\end{mylem}
\begin{mylem}
Consider a second-order system:
\begin{align}
\begin{split}
\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding surface}
\end{split}
\end{align}
and oen can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
%since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
\begin{align}
%t_s\le t_0+\frac{2(x_1^2+x_2^2)^{1-\alpha}}{1-\alpha}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{1-\alpha},
\end{align}
where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding surface}) obtains:
\begin{align}
\dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding surface}
\end{align}
the convergence time of which is
\begin{align}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{d(1-\alpha)}.
\end{align}\label{lemma:2}
\end{mylem}
\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are addressed according the following to theorem.}
\begin{mythm}\label{theorem:1}DTSM Controller Design. The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as follows:
\begin{align}
\begin{split}
u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),\label{eq:DSM input}
\end{split}
\end{align}
where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value.
\end{mythm}
\begin{proof}
\textcolor{red}{For the system~(\ref{eq:second-order system}) with the SM surface~(\ref{eq:dual sliding surface}), according to the equivalent control technique and the sliding surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
\begin{align}\begin{split}
u_1 &= u_{eq1}+u_{sw1}\\
u_2 &= u_{eq2}+u_{sw2}\notag
\end{split}\end{align}
where
\begin{align}\begin{split}
u_{eq1} &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
u_{eq2} &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2)\notag
\end{split}\end{align}
are the eauivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$. The switching inputs are designed as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding surface.}

Considering the Lyapunov function $V=\frac{1}{2}{\bm s}^T\bm s$, its derivative can be written as

@@

Substituting inputs (\ref{eq:DSM input}) in~Eq.~(\ref{eq:V_1}) yields

@@

Hence, the system (\ref{eq:second-order system}) converges to the desired SM surface (\ref{eq:dual sliding surface}), and incidentally the convergence time can be calculated according to the finite time convergence theory. Once the system (\ref{eq:second-order system}) satisfies $\bm s = \bm 0$, the entire system states will be handled by the reduced system:

@@

where $\hat V = \frac{x_1^2+x_3^2}{2}$ is the Lyapunov function selected for the reduced system. $t_r$ and $t_s$ stand for the reaching time and the sliding time, respectively. This completes the proof.}

@@

On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the SM surface design to improve the performance of the reaching phase, and furthermore this modified method makes the design process more flexible. Consider the system~(\ref{eq:second-order system}) with the surface $\bm s = [s_1,s_2]^T$ described by following expressions:

@@

s_1 &= x_2+\gamma(\vert x_1\vert^{\alpha} sgn(x_1)+x_1^3)-\lambda x_3\\
s_2 &= x_4+\gamma(\vert x_3\vert^{\alpha} sgn(x_3)+x_3^3)+\lambda x_1,\label{eq:modified dual sliding surface}

@@

where $\gamma$ is a positive constant and $\lambda\in R$ is a design parameter. Accordingly, the modified DTSM control inputs are formed in the following theorem.
\begin{mythm}\label{theorem:2}Modified DTSM Controller Design.
The second-order system (\ref{eq:second-order system}) will reach the desired SM surface $\bm s = \bm 0$ shown in~Eq.~(\ref{eq:modified dual sliding surface}) in finite time, and then the system states will converge to zero along the surface $\bm s=\bm 0$ in finite time, if the inputs are designed as follows:

@@

In the MDTSM scheme, the performances of the reaching and sliding phases can benefit from suitably selected $\lambda$ and $\gamma$ analytically. The establishment of $V(t_0)$ is depended on $\lambda$, if the state $\bm x(t_0)$ has been fixed. Exactly, $\lambda$ affects the reaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V=\bm s^T\bm s = \bm 0,\forall t\ge t_r$. $\eta$ is definied as the reaching speed, because a suitable $\eta$ can adjust the reaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the reaching phase dynamics, and similarly $\gamma$ is defined as the management parameter of the sliding phase dynamics.

@@

For the proposed designs, the parameter $\gamma$ may be defined as different scalars for the inputs, if so, one can produce the total convergence time as:

@@

\subsection{Nonsingular MDTSM controller design}

The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal SMC, there exists another obstacle in the design mentioned above, i.e., the issue of the singularity in control inputs. Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition). For coping with the singularity, the nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.

@@

Considering the second-order system (\ref{eq:second-order system}), the TSM surfaces are designed as:

@@

and nonsingular inputs can be given out directly as follows:

@@

$sat(u_f,u_s)$ is a saturation function:

@@

-u_s\quad &u_f\le -u_s\label{eq:saturation}

@@

with $u_s>0$. Adopting the control scheme mentioned above, the system~(\ref{eq:second-order system}) will be stabilized in finite time without any singularity occurring during the regulation process.

@@

Consider a second-order system (\ref{eq:second-order system}), and for eliminating the singularity, the inputs are selected to complete the nonsingular MDTSM scheme. Introducing the saturation terms~\ref{eq:saturation} into the original inputs yields:

@@

and one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:second-order system}), providing the finite time convergence by using MDTSM technique.

@@

\subsection{MDTSM controller design for systems subjected to input limitations}

@@

Besides singularity issue, in practice, the control input can not be very large due to the input limitation, such as the tension limitation in the deployment of the tethered satellite system~\cite{Ma201667}, and hence it is meaningful to adapt the proposed controllers for the system subjected to the input limitation. Consider a nominal second-order system subjected to the input limitation:

@@

Thanks to the above assumption, we give out the adaptive DTSM scheme.

@@

Consider the nonlinear system described as:

@@

where the conditions of variables are same to the system~(\ref{eq:second-order system}). Construct the SM surfaces as:

@@

where $c_1$ and $c_2$ are suitable positive constants, and $s_1$ and $s_2$ have been defined in Eq.~(\ref{eq:dual sliding surface}). Adopting the equivalent control design method deduces the individual equivalent inputs:
